Optimizing the Robotics Closet

### 2018-11-16 paper.tex
w0w rip metal boi closet

\section{Assumptions}
Most items in the robotics closet are in boxes. As a result, we assume that all
items are rectangular prisms. Although items such as the chemicals or soldering irons
are not strictly rectangle-shaped, it would be strange for another item reached into
the empty areas of the items' bounding boxes. Taking advantage of this, we approximate
all items as being rectangular prisms, and measure their bounding boxes.
\par
\textbf{\color{red} TODO: Fill in the rest of the assumptions}

>>>>

\section{Assumptions}
Most items in the robotics closet are in boxes. As a result, we assume that all
items are rectangular prisms. Although items such as the chemicals or soldering irons
are not strictly rectangle-shaped, it would be strange for another item reached into
the empty areas of the items' bounding boxes. Taking advantage of this, we approximate
all items as being rectangular prisms, and measure their bounding boxes.
\par
We also assumed that certain parts of the robotics closet are not to be moved. For example, the shelf containing aluminum brackets and blocks for machining was excluded from the model entirely. This is due to the cumbersome nature of moving hundreds of unboxed chunks of metal, and due to opposition to its transportation by team members who frequently use it. The food pantry portion as well as some non-food items that made their way into it was similarly excluded after brief deliberation. Excluding parts of the closet from the model does not reduce the validity of the remaining optimization since 
\textbf{\color{red} TODO: Fill in the rest of the assumptions}
